Future challenges for Research Software Engineering

### 2025-05-17 future_challenges_for_RSEng.tex
fix preposition
capitalise
swap verb

\begin{story}{The greater world of Kim and Kay}{ethics}
10 years have passed since Kim and Kay started on their journey of being RSEs. Back then,
at the universities of Eden and Utopia, life was more orderly and harmonious. Kay is now working in a project that develops
software for cheap water monitoring devices in the global south. Kim is currently designing the software service stack
at the university, and increasingly struggles to find compelling Open Source alternatives that enables them keep complete control of their data
rather than relying on software and tools that are backed by large corporate entities. So far she still has the support of the university board, since it values
strategic autonomy.
Her son Kyle on the other hand started out with a degree in Physics and then took one of the newly created RSE Master's courses,
but quickly decided that work in academia with its time limited contracts is not attractive.
Governments around the world are struggling to reposition themselves in this emerging de-globalised world with its new blocks
and therefore have de-prioritised publicly funded research. Kyle decided to go to an defence company since they offer
more secure employment in this polarized world.
\end{story}

>>>>

\begin{story}{The greater world of Kim and Kay}{ethics}
10 years have passed since Kim and Kay started on their journey of being RSEs. Back then,
at the universities of Eden and Utopia, life was more orderly and harmonious. Kay is now working on a project that develops
software for cheap water monitoring devices in the Global South. Kim is currently designing the software service stack
at the university, and increasingly struggles to find compelling Open Source alternatives that enables them keep complete control of their data
rather than relying on software and tools that are backed by large corporate entities. So far she still has the support of the university board, since it values
strategic autonomy.
Her son Kyle on the other hand started out with a degree in Physics and then took one of the newly created RSE Master's courses,
but quickly decided that work in academia with its time limited contracts is not attractive.
Governments around the world are struggling to reposition themselves in this emerging de-globalised world with its new blocks
and therefore have de-prioritised publicly funded research. Kyle decided to work for a defence company since they offer
more secure employment in this polarized world.
\end{story}
